\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/related-work.tex
minor changes

Spectre builds upon prior work on cache side channels, and similarly uses to to
leak information from
processes~\cite{percival2005cache,zhang2012cross,osvik2006cache}. In \speculake,
we use the branch predictor as a \emph{covert channel}~\cite{lampson1973note}
between the trigger program and malware payload, allowing the malware's
(speculative) execution path to be influenced by the trigger.

>>>>

Spectre builds upon prior work on cache side channels, and similarly uses them
to leak information from
processes~\cite{percival2005cache,zhang2012cross,osvik2006cache}. In \speculake,
we use the branch predictor as a \emph{covert channel}~\cite{lampson1973note}
between the trigger program and malware payload, allowing the malware's
(speculative) execution path to be influenced by the trigger.
